Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on natural Nb and Cu

### 2017-12-08 nb_px_paper/nb_px_paper.tex
Squashed my comments

\comment{Confirm beam parameters below, from notebook}

This target stack was assembled and irradiated at the Isotope Production Facility (IPF) at the Los Alamos National Laboratory (LANL), using the LANSCE linear accelerator. 
The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a \textred{100 \micro s pulse at a frequency of 1 Hz}, for an anticipated integral current of 205.9 nAh.
The proton beam incident upon the stack's Inconel beam entrance window had a calculated energy of 100 MeV, with an approximately Gaussian energy distribution width of 0.1 MeV - this energy profile was used for all later analysis.
At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
The activated foils were cleaned of all surface contamination, and transported to a counting lab for decay spectroscopy, which started approximately 7 hours following end-of-beam.

@@

\comment{get citation data for UNISAMPO}

Following activation, the Al, Cu, and Nb foils  were  transferred to the LANL TA-48 counting lab, where their induced activities could be measured via gamma ray spectroscopy.
For consistency, a single detector was used in this measurement, an ORTEC GEM Series  High-Purity Germanium (HPGe) detector.
The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
Samples were counted at fixed positions ranging 4.5 - 83.5  cm from the front face of the detector, with a series of standard calibration sources used to determine in-house energy, efficiency, and pileup calibrations for each position.
The foils were counted for a period of 2 weeks following EoB, to accurately quantify all induced activities.
An example gamma ray spectrum collected in such a fashion is shown in \autoref{fig:gspec}.
For all spectra collected, net peak areas were fitted using the gamma spectroscopy analysis code UNISAMPO \textred{(add UNISMPO citation)}, which has been shown to perform best in head-to-head comparisons with other common analysis codes \cite{Jackman2014}, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.

@@

\comment{Add 1st and 2nd order bateman stuff here, maybe cite Cetnar2006 also }

@@

To convert these activities into cross sections, corrections must be made for the decay of the various reaction products in  between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB.
The use of  multiple gamma rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma ray observation.
For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points $t$ (since EoB) to the well-known radioactive decay law.
% \begin{equation}
% A\pp{t} = A_0 e^{-\lambda t}
% \end{equation}
Nonlinear regression was used for this fitting process, minimizing on $\chi^2$ / degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ would be reported as as well.
As with the gamma ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation:
\begin{equation}
A_n\pp{t} = \lambda_n \sum_{i=1}^n \left[  N_i\pp{0} \times \pp{\prod_{j=i}^{n-1}\lambda_j} \times \pp{\sum_{j=i}^n \dfrac{e^{-\lambda_j t}}{\prod_{i\neq j}^n \pp{\lambda_i - \lambda_j}}  }   \right]
\end{equation}
While higher-order terms were added if needed, typically for an isomeric state in a particular mass chain,  the second-order expansion ($n=2$) was often sufficient to quantify EoB activities in a mass chain, simplifying to:
\begin{equation}
A_2\pp{t} = \dfrac{A_{1,0}\lambda_2}{\lambda_1 - \lambda_2} \pp{e^{-\lambda_2 t} - e^{-\lambda_1 t}} + A_{2,0} e^{-\lambda_2 t}
\end{equation}
In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, that the feeding contributions from decay could be separated and an independent cross section reported.
After quantifying the cumulative EoB activities at the top of a mass chain and all subsequent independent EoB activities, these will be later used to report the various cross sections for all observed reaction products and isomeric states.

@@

\comment{Add missing citations here}

The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in differential proton fluence.
Of these, the first four contributions are all easily quantified in the preparation and execution of a stacked target irradiation;  the last two contributions prove to be more nuanced, however.
The uncertainty in proton fluence for irradiated monitor foils is derived from statistical uncertainty in the modeling of proton transport in the stack irradiation, discussed in \autoref{sec:proton_transport}.
The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
Fortunately, the recommended cross section values for each monitor reaction tend to match one of the   selected experimental data sets used in their evaluation almost perfectly.
Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
For the monitor reactions employed in this work, these data sets are G. Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \textred{(insert Steyn citation here)}, M. Uddin (2004) for \ce{^{nat}Al}(p,x)\ce{^{24}Na} \cite{Uddin2004}, and S. Mills (1992) for \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} \cite{Mills1992}.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
\label{tab:cu_rp_table}
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllllll@{}}
\toprule
                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7} 
E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
\ce{^{51}Cr}\,($\sigma_c$)    & $0.888\pm0.058$         & $0.361\pm0.015$         & $0.440\pm0.019$         & $0.2949\pm0.0070$       & \hrulefill              & \hrulefill              \\
\ce{^{52}Mn}\,($\sigma_c$)    & $1.640\pm0.042$         & $0.552\pm0.014$         & $0.0398\pm0.0012$       & $0.00513\pm0.00051$     & \hrulefill              & \hrulefill              \\
\ce{^{52g}Mn}\,($\sigma_i$)   & $0.650\pm0.018$         & $0.231\pm0.013$         & $0.0160\pm0.0021$       & $0.000961\pm0.000027$   & \hrulefill              & \hrulefill              \\
\ce{^{52m}Mn}\,($\sigma_i$)   & $0.989\pm0.037$         & $0.321\pm0.020$         & $0.0238\pm0.0032$       & $0.00417\pm0.00043$     & \hrulefill              & \hrulefill              \\
\ce{^{54}Mn}\,($\sigma_c$)    & $5.67\pm0.15$           & $3.65\pm0.11$           & $4.05\pm0.11$           & $4.71\pm0.12$           & $1.656\pm0.042$         & \hrulefill              \\
\ce{^{55}Co}\,($\sigma_c$)    & $1.656\pm0.048$         & $0.983\pm0.030$         & $0.1892\pm0.0076$       & $0.0291\pm0.0024$       & $0.00231\pm0.00019$     & \hrulefill              \\
\ce{^{56}Ni}\,($\sigma_c$)    & $0.0779\pm0.0022$       & $0.0973\pm0.0025$       & $0.0886\pm0.0022$       & $0.02967\pm0.00079$     & \hrulefill              & \hrulefill              \\
\ce{^{57}Ni}\,($\sigma_c$)    & $1.416\pm0.039$         & $1.164\pm0.030$         & $1.370\pm0.033$         & $2.074\pm0.051$         & $1.543\pm0.035$         & $0.02638\pm0.00077$     \\
\ce{^{57}Co}\,($\sigma_i$)    & $38.78\pm0.99$          & $34.42\pm0.84$          & $35.06\pm0.81$          & $47.3\pm1.1$            & $47.0\pm1.1$            & $3.227\pm0.081$         \\
\ce{^{58}Co}\,($\sigma_c$)    & $55.7\pm3.5$            & $53.2\pm4.1$            & $41.8\pm2.9$            & $32.8\pm2.5$            & $38.4\pm3.4$            & $62.7\pm3.4$            \\
\ce{^{58g}Co}\,($\sigma_i$)   & $13.6\pm2.3$            & $10.5\pm1.9$            & $5.9\pm1.6$             & $7.6\pm1.3$             & $7.0\pm1.7$             & $1.13\pm0.31$           \\
\ce{^{58m}Co}\,($\sigma_i$)   & $42.2\pm2.7$            & $42.8\pm3.6$            & $35.8\pm2.5$            & $25.2\pm2.1$            & $31.5\pm2.9$            & $61.6\pm3.4$            \\
\ce{^{59}Fe}\,($\sigma_c$)    & $0.836\pm0.027$         & $0.810\pm0.022$         & $0.733\pm0.020$         & $0.601\pm0.017$         & $0.206\pm0.010$         & $0.93\pm0.15$           \\
\ce{^{60}Co}\,($\sigma_c$)    & $12.79\pm0.43$          & $13.04\pm0.42$          & $10.89\pm0.78$          & $11.15\pm0.58$          & $9.17\pm0.74$           & $6.7\pm1.0$             \\
\ce{^{61}Cu}\,($\sigma_c$)    & $48.8\pm1.5$            & $54.4\pm1.7$            & $63.7\pm2.1$            & $70.3\pm2.1$            & $79.5\pm2.7$            & $158.2\pm3.2$           \\
\ce{^{64}Cu}\,($\sigma_c$)    & $37.4\pm1.4$            & $41.4\pm1.2$            & $44.5\pm1.7$            & $49.0\pm1.5$            & $54.9\pm1.4$            & $63.7\pm1.6$            \\ \bottomrule
\end{tabular}
}
\end{table}

@@

\section{Decay data} \label{data}
% 
% % \begin{longtable}{|c|c|c|c|c|} 
% % \caption{My caption}
% % \label{tab:dummy}
% % % \begin{tabular}{|c|c|c|c|c|}
% %    \hline
% %  
% % \end{longtable}
Table of decay data  for observed gamma rays. 
The  values for lifetime and gamma ray branching ratios  listed here were used in all calculations of measured cross sections \cite{Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012}.

\comment{add citation for NDS A=22,24,93}

@@

Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \textred{(cite me!)}, and the reaction modeling codes EMPIRE-3.2.3 and TALYS-1.8 \cite{Koning2012}.

\comment{add EMPIRE citation here!}

\comment{add TENDL citation here!}

\comment{Fix a few figure labels (c/i) based on Jon;s email}

>>>>

This target stack was assembled and irradiated at the Isotope Production Facility (IPF) at the Los Alamos National Laboratory (LANL), using the LANSCE linear accelerator. 
The stack was irradiated for approximately 2 hours with a nominal current of 1 mA, using a 50 \micro s pulse at a frequency of 2 Hz, for an anticipated integral current of 205.9 nAh.
The proton beam incident upon the stack's Inconel beam entrance window had a calculated energy of 100 MeV, with an approximately Gaussian energy distribution width of 0.1 MeV - this energy profile was used for all later analysis.
At the end of the irradiation, the target stack was withdrawn from the beamline into the IPF hot cell, where it was disassembled and the activated foils removed using robotic manipulators.
The activated foils were cleaned of all surface contamination, and transported to a counting lab for decay spectroscopy, which started approximately 7 hours following end-of-beam.

@@

Following activation, the Al, Cu, and Nb foils  were  transferred to the LANL TA-48 counting lab, where their induced activities could be measured via gamma ray spectroscopy.
For consistency, a single detector was used in this measurement, an ORTEC GEM Series  High-Purity Germanium (HPGe) detector.
The detector is a mechanically-cooled coaxial p-type HPGe with a 1 mm aluminum window, and a 49.2 mm diameter, 27.9 mm long crystal.
Samples were counted at fixed positions ranging 4.5 - 83.5  cm from the front face of the detector, with a series of standard calibration sources used to determine in-house energy, efficiency, and pileup calibrations for each position.
The foils were counted for a period of 2 weeks following EoB, to accurately quantify all induced activities.
An example gamma ray spectrum collected in such a fashion is shown in \autoref{fig:gspec}.
For all spectra collected, net peak areas were fitted using the gamma spectroscopy analysis code UNISAMPO \cite{Aarnio2001}, which has been shown to perform best in head-to-head comparisons with other common analysis codes \cite{Jackman2014}, due to its peak fitting algorithms and incorporation  of calibrated detector-specific peak shapes and widths.

@@

@@

To convert these activities into cross sections, corrections must be made for the decay of the various reaction products in  between EoB and the spectrum acquisition, in order to calculate $A_0$, the initial activity at EoB.
The use of  multiple gamma rays at multiple points after EoB to calculate initial activities  for each observed product nucleus allows for a more accurate  determination of $A_0$ than simply basing its calculation off of a single gamma ray observation.
For the case of cumulative cross sections, EoB activities were quantified by fitting the activities observed at multiple time points $t$ (since EoB) to the well-known radioactive decay law.
% \begin{equation}
% A\pp{t} = A_0 e^{-\lambda t}
% \end{equation}
Nonlinear regression was used for this fitting process, minimizing on $\chi^2$ / degree of freedom, so that not only would the uncertainty-weighted EoB activities be fitted, but that a 1-$\sigma$ confidence interval in $A_0$ would be reported as as well.
As with the gamma ray intensities, all lifetimes used in this work are tabulated in \autoref{tab:nudat_table_monitors} and \autoref{tab:nudat_table_nb} of \ref{data}.
In the case of independent cross sections, a similar process was followed, quantifying $A_i\pp{0} = A_{i,0}$, the EoB activity of nuclide $i$, by instead regressing to the solutions to the Bateman equation \cite{bateman1910solution,Cetnar2006}:
\begin{equation}
A_n\pp{t} = \lambda_n \sum_{i=1}^n \left[  N_i\pp{0} \times \pp{\prod_{j=i}^{n-1}\lambda_j} \times \pp{\sum_{j=i}^n \dfrac{e^{-\lambda_j t}}{\prod_{i\neq j}^n \pp{\lambda_i - \lambda_j}}  }   \right]
\end{equation}
While higher-order terms were added if needed, typically for an isomeric state in a particular mass chain,  the second-order expansion ($n=2$) was often sufficient to quantify EoB activities in a mass chain, simplifying to:
\begin{equation}
A_2\pp{t} = \dfrac{A_{1,0}\lambda_2}{\lambda_1 - \lambda_2} \pp{e^{-\lambda_2 t} - e^{-\lambda_1 t}} + A_{2,0} e^{-\lambda_2 t}
\end{equation}
In these cases, the previously-quantified EoB activities from decay precursors ($A_{1,0}$, etc) would be substituted in, that the feeding contributions from decay could be separated and an independent cross section reported.
After quantifying the cumulative EoB activities at the top of a mass chain and all subsequent independent EoB activities, these will be later used to report the various cross sections for all observed reaction products and isomeric states.

@@

The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in differential proton fluence.
Of these, the first four contributions are all easily quantified in the preparation and execution of a stacked target irradiation;  the last two contributions prove to be more nuanced, however.
The uncertainty in proton fluence for irradiated monitor foils is derived from statistical uncertainty in the modeling of proton transport in the stack irradiation, discussed in \autoref{sec:proton_transport}.
The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
Fortunately, the recommended cross section values for each monitor reaction tend to match one of the   selected experimental data sets used in their evaluation almost perfectly.
Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
For the monitor reactions employed in this work, these data sets are G. Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \cite{Steyn1990}, M. Uddin (2004) for \ce{^{nat}Al}(p,x)\ce{^{24}Na} \cite{Uddin2004}, and S. Mills (1992) for \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} \cite{Mills1992}.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}
\centering
\caption{Measured cross sections for the various \ce{^{nat}Cu}(p,x) reaction products observed in this work. Cumulative cross sections are designated as $\sigma_c$, independent cross sections are designated as $\sigma_i$.}
\label{tab:cu_rp_table}
\small
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}lllllll@{}}
\toprule
                            & \multicolumn{6}{c}{Production cross section (mb)}                                                                                                         \\ \cmidrule(l){2-7} 
E$_\text{p}$ (MeV)          & $89.74^{+0.48}_{-0.43}$ & $79.95^{+0.67}_{-0.64}$ & $70.17^{+0.91}_{-0.85}$ & $61.58^{+1.03}_{-0.98}$ & $52.10^{+1.25}_{-1.20}$ & $41.05^{+1.62}_{-1.54}$ \\ \midrule
\ce{^{51}Cr}\,($\sigma_c$)    & $0.888\pm0.058$         & $0.361\pm0.015$         & $0.440\pm0.019$         & $0.2949\pm0.0070$       & \hrulefill              & \hrulefill              \\
\ce{^{52}Mn}\,($\sigma_c$)    & $1.640\pm0.042$         & $0.552\pm0.014$         & $0.0398\pm0.0012$       & $0.00513\pm0.00051$     & \hrulefill              & \hrulefill              \\
\ce{^{52g}Mn}\,($\sigma_i$)   & $0.650\pm0.018$         & $0.231\pm0.013$         & $0.0160\pm0.0021$       & $0.000961\pm0.000027$   & \hrulefill              & \hrulefill              \\
\ce{^{52m}Mn}\,($\sigma_i$)   & $0.989\pm0.037$         & $0.321\pm0.020$         & $0.0238\pm0.0032$       & $0.00417\pm0.00043$     & \hrulefill              & \hrulefill              \\
\ce{^{54}Mn}\,($\sigma_c$)    & $5.67\pm0.15$           & $3.65\pm0.11$           & $4.05\pm0.11$           & $4.71\pm0.12$           & $1.656\pm0.042$         & \hrulefill              \\
\ce{^{55}Co}\,($\sigma_c$)    & $1.656\pm0.048$         & $0.983\pm0.030$         & $0.1892\pm0.0076$       & $0.0291\pm0.0024$       & $0.00231\pm0.00019$     & \hrulefill              \\
\ce{^{56}Ni}\,($\sigma_c$)    & $0.0779\pm0.0022$       & $0.0973\pm0.0025$       & $0.0886\pm0.0022$       & $0.02967\pm0.00079$     & \hrulefill              & \hrulefill              \\
\ce{^{57}Ni}\,($\sigma_c$)    & $1.416\pm0.039$         & $1.164\pm0.030$         & $1.370\pm0.033$         & $2.074\pm0.051$         & $1.543\pm0.035$         & $0.02638\pm0.00077$     \\
\ce{^{57}Co}\,($\sigma_i$)    & $38.78\pm0.99$          & $34.42\pm0.84$          & $35.06\pm0.81$          & $47.3\pm1.1$            & $47.0\pm1.1$            & $3.227\pm0.081$         \\
\ce{^{58}Co}\,($\sigma_c$)    & $55.7\pm3.5$            & $53.2\pm4.1$            & $41.8\pm2.9$            & $32.8\pm2.5$            & $38.4\pm3.4$            & $62.7\pm3.4$            \\
\ce{^{58g}Co}\,($\sigma_i$)   & $13.6\pm2.3$            & $10.5\pm1.9$            & $5.9\pm1.6$             & $7.6\pm1.3$             & $7.0\pm1.7$             & $1.13\pm0.31$           \\
\ce{^{58m}Co}\,($\sigma_i$)   & $42.2\pm2.7$            & $42.8\pm3.6$            & $35.8\pm2.5$            & $25.2\pm2.1$            & $31.5\pm2.9$            & $61.6\pm3.4$            \\
\ce{^{59}Fe}\,($\sigma_c$)    & $0.836\pm0.027$         & $0.810\pm0.022$         & $0.733\pm0.020$         & $0.601\pm0.017$         & $0.206\pm0.010$         & \hrulefill        \\
\ce{^{60}Co}\,($\sigma_c$)    & $12.79\pm0.43$          & $13.04\pm0.42$          & $10.89\pm0.78$          & $11.15\pm0.58$          & $9.17\pm0.74$           & $6.7\pm1.0$             \\
\ce{^{61}Cu}\,($\sigma_c$)    & $48.8\pm1.5$            & $54.4\pm1.7$            & $63.7\pm2.1$            & $70.3\pm2.1$            & $79.5\pm2.7$            & $158.2\pm3.2$           \\
\ce{^{64}Cu}\,($\sigma_c$)    & $37.4\pm1.4$            & $41.4\pm1.2$            & $44.5\pm1.7$            & $49.0\pm1.5$            & $54.9\pm1.4$            & $63.7\pm1.6$            \\ \bottomrule
\end{tabular}
}
\end{table}

@@

\section{Decay data} \label{data}
% 
% % \begin{longtable}{|c|c|c|c|c|} 
% % \caption{My caption}
% % \label{tab:dummy}
% % % \begin{tabular}{|c|c|c|c|c|}
% %    \hline
% %  
% % \end{longtable}
Table of decay data  for observed gamma rays. 
The  values for lifetime and gamma ray branching ratios  listed here were used in all calculations of measured cross sections \cite{Basunia2015,Firestone2007,Wang2017,Dong2015,Dong2014,JUNDE2008787,Junde2011,Bhat1998,Nesaraja2010,BAGLIN2002,Browne2013,Zuber20151,NICHOLS2012973,Singh2007,Browne2010,Tuli2003,McCutchan2015,Singh2014,NEGRET20151,Johnson2015,McCutchan2014,Singh2013,Browne1997,Baglin2013,Baglin2012,Baglin2011}.

@@

Figures of the cross sections measured in this work are presented here, in comparison with literature data \cite{Albouy1963,PhysRev.162.1055,PhysRevC.6.1235,Grutter1982,Greenwood1984,Aleksandrov1987,levkovski1991cross,Mills1992,MICHEL1997153,Fassbender1997,Ido2002,sisterson2002selected,YashimaH2003,A2006,Ditroi2008,Ditroi2009,steyn2011excitation,Titarenko2011,Shahid2015,Garrido2016,Graves2016}, the TENDL-2015 data library \cite{Koning2012}, and the reaction modeling codes EMPIRE-3.2.3 and TALYS-1.8 \cite{Herman2007,Koning2012}.

% \comment{Fix a few figure labels (c/i) based on Jon;s email}
